\mytitile\\~

### 2019-12-23 document.tex
Updates

% ****** Start of file aipsamp.tex ******
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.
%
%   See the AIP README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
% 
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aipsamp
%  2)  bibtex aipsamp
%  3)  latex  aipsamp
%  4)  latex  aipsamp
%
% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 pra,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
]{revtex4-1}

@@

\renewcommand*{\figureautorefname}{Fig.}

\newcommand{\mytitile}{Effects of strong interaction between light and matter in a superconducting artificial molecule}

@@

	\title[\mytitile]{\mytitile\\~}

	\author{G.P. Fedorov}
	\email{gleb.fedorov@phystech.edu}

	\affiliation{ 
		Russian Quantum Center, Skolkovo village, Russia
	}%
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}
	\affiliation{
		National University of Science and Technology MISiS, Moscow, Russia
	}%
	\author{V.B. Yursa}
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}%

@@

	\author{O.V. Astafiev}
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia 
	}%

@@

	\begin{abstract}
	Since their demonstration, superconducting artificial atoms have been extensively used for studies in quantum optics. Their particular advantages compared to natural systems are the strong coupling to radiation and the high level of control over their state; these properties open the way to previously unexplored physics. In this work, we have irradiated a superconducting artificial molecule composed of two flux-tunable transmons with intense light while monitoring its state via joint dispersive readout. At certain configurations of its energy levels, the molecule has demonstrated a complex spectrum deviating qualitatively from the stationary solution. However, it was reproduced accurately by numerical simulations, and turned out to be a consequence of a modified Autler-Townes effect when a single tone is simultaneously dressing the system and probing the transitions between new eigenstates. To quantify this effect, self-consistent models were employed accounting for both these processes at the same time. We note that this study is an important step towards understanding the behaviour of more complex systems of many atoms interacting with strong radiation.
	\end{abstract}

@@

Over the past twenty years, superconducting artificial atoms (SAA) were used in numerous experiments confidently demonstrating the validity of fundamental quantum mechanical laws\cite{you2011atomic}. Due to synthetic nature of SAA, their Hamiltonians can be pre-designed and engineered, and this makes them a particularly versatile tool for studies in quantum optics. Notably, their parameters may be varied in such a wide range that novel physical effects previously inaccessible for natural systems may be directly observed. For example, the strong coupling regime, when the coupling strength between light and a quantum system approaches 1\% of their frequency, has been a major challenge for atoms, molecules, etc and was only reached using high-finesse cavities. In contrast, superconducting quantum systems have rapidly attained this milestone using \textit{circuit QED}\cite{wallraff2004strong} just in a few years after their first demonstration\cite{chiorescu2004coherent} and have already surpassed other strongly-coupled systems in terms of coherence\cite{forn2019ultrastrong}. 
Moreover, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strongly to the free-propagating electromagnetic waves in 1D on-chip waveguides\cite{astafiev2010resonance} without using cavities at all. The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is already the ultra-strong coupling regime\cite{forn2019ultrastrong}.

Strong interaction of a quantum system with light lead to various phenomena explained by resonant single- and multi-photon excitation of transitions between energy levels. The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (A-T) splitting\cite{autler1955stark}.

In this work, we study effects of light-matter interaction that occur in a system of two coupled artificial atoms: a superconducting artificial molecule\cite{kou2017fluxonium} (SAM). In our experiment, we use two X-mons\cite{barends2013coherent} interacting with each other through a cavity bus\cite{majer2007coupling}. Microwave radiation is applied to this system through a coplanar on-chip antenna and transmon states may be monitored by dispersive readout using the same coupling cavity \cite{chow2010detecting}.

It turns out that due to the strong interaction of SAM with the microwave drive, multiphoton transitions and the Autler-Townes effect are playing the crucial role in the phenomena that we observe. The A-T splitting has been observed before in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and for SAA as well\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}. However, the previous studies have  only involved just a single SAA and have demonstrated only the standard spectral signatures known from the quantum optics (see Appendix \ref{sec:3-level-at}); instead, a diatomic SAM allows to observe some qualitatively new spectral manifestations of the effect. Remarkably, besides its fundamental value, this experiment may be useful for future quantum computers: a quantum engineer should consider the observed behaviours as unwanted, and thus careful control of the driving power must be employed to avoid them (for instance, as we will show, the bSWAP gate\cite{poletto2012entanglement} is directly affected).

The manuscript consists of four main parts and an Appendix. Section I is this introduction; Section II is devoted to the approaches that were used in our study; Section III contains the results of our experimental and theoretical research; finally, in Section IV we make a conclusion of our work and discuss future prospects. The Appendix contains important details of the theoretical framework that we use.

@@

\subsection{Device design and fabrication}
We have designed the SAM as a pair of transmon (Xmon\cite{barends2013coherent}) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator ($\omega_r/2\pi \equiv f_r = 7$ GHz, $\kappa = 1/100\ \text{ns}^{-1}$) which both couples\cite{majer2007coupling} the qubits and allows the joint\cite{chow2010detecting} readout of their states. In \autoref{fig:experiment}~(a), the optical photograph of the device is shown depicting the layout of the components. The resonator in its upper part is connected to a coplanar waveguide through which the readout is performed. In its lower part, it is coupled to the transmons by a dual ``claw''\cite{barends2013coherent} coupler. Flux lines that allow independent control of the transmon frequencies are coming from the sides. Finally, the excitation waveguide coming from below directs microwave signal towards the SAM. In \autoref{fig:experiment}~(b) the equivalent electrical circuit of the device. The resonator fundamental mode is approximated as an LC-circuit (in the middle), the transmons are shown in colour on the sides as the LC-circuits as well, but with tunable non-linear inductances. A capacitively coupled excitation line is also shown in green. Finally, in \autoref{fig:experiment}~(c) we show schematically the frequencies of the transmons depending on the external magnetic flux. Since an effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue). Using both coils, it is possible to align them so that the lower sweet-spot of the orange transmon is just below the upper sweet-spot of the blue transmon (see the dashed rectangle,  \autoref{fig:experiment}~(c)). This configuration is chosen as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are close to each other in frequency. Additionally, the transmons are better protected from the flux noise in this area being close to their sweet spots.

The fabrication process...

@@

\begin{table}
	\begin{ruledtabular}
	\begin{tabular}{rll}
	Parameter & Transmon 1  & Transmon 2\\\hline
	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
	$\alpha/2\pi$ [MHz] & 220 & 220 \\
	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
	$J/2\pi$ [MHz] &\multicolumn{2}{c}{10} 
	\end{tabular}
	\end{ruledtabular}
	\caption{SAM parameters. Transmons are only different in the frequency tuning range and coherence times measured in the lower sweet spot for the 1\textsuperscript{st} one and in the higher sweet spot for the 2\textsuperscript{nd}.}
\end{table}

@@

Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
\end{equation}
where $\hat H_{int} = \hbar J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms. In the following, we will also transform \eqref{Hsystem} into the frame rotating with both drives by an operator
\begin{align}
&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}\\
&\hat H_R = \hat R^{\dagger}\hat H \hat R -	 {i}\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
\end{align}
Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA
\begin{equation}
\begin{aligned}
	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
	\hat H_{int} &\rightarrow \hbar J \left[\hat b^\dag \hat c e^{(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{-(\omega_d^1 - \omega_d^2)t}\right],\\
	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

Besides the unitary evolution, we take into account the incoherent processes of relaxation and dephasing for each transmon. They are modelled using the Lindblad equation with the following collapse operators:
\begin{equation}\
\begin{split}
\hat{{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
\hat{{O}}_{\phi, 1} = \sqrt{2\gamma_{\phi,1}}\, \hat b^\dag \hat b,\\
\hat{{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
\hat{{O}}_{\phi,2} = \sqrt{2\gamma_{ \phi,2}}\, \hat c^\dag \hat c.
\end{split}
\end{equation}
As one can see, the collapse operators are in a separable form, i.e. acting only upon a single transmon each. This is a valid approach until the coupling strength $J$ is not too large\cite{beaudoin2011dissipation}. Therefore, the complete evolution equation for the system density matrix $\hat \rho$ is
\begin{equation}
\partial_t \hat \rho = \frac{i}{\hbar}[\hat \rho, \hat H] + \sum_{\alpha, i} \mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho = \mathcal{L}\hat\rho, \label{eq:master}
\end{equation}
where $\mathcal{D}[\hat{{O}}]\hat \rho = \hat{{O}} \hat \rho \hat{{O}}^\dag - \frac{1}{2}\{ \hat{{O}}^\dag \hat{{O}}, \hat \rho\}$ and $\mathcal{L}$ is the Liouville superoperator or the Liouvillian.

@@

Numerical simulations are crucial for studying the equation \eqref{eq:master} since is does not allow  analytical solution. Therefore, we have been using the \textit{qutip}\cite{johansson2013qutip} (quantum optics toolbox) to simulate the dynamics and find the steady state of the system for various parameter combinations of the Liouvillian.

Two distinct modes of simulation were used during the modelling. The first one is for the Liouvillians that do not explicitly depend on time (stationary case). In this case, the steady state $\hat \rho_{ss}$ of the system should be calculated from the set of linear equations obtained from \eqref{eq:master}
\begin{equation}
\partial_t \hat \rho = 0 = \mathcal{L} \hat \rho
\end{equation}
This equation is solved with the qutip's \textit{steadystate} function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}. This method is applicable when the driving of the two transmons is at the same frequency since from \eqref{eq:RWA} follows that $\hat H_{int}$ becomes time independent when $\omega_d^1 = \omega_d^2$.

The second mode is required when it is not possible to avoid the time-dependence of the Liouvillian. This is the case when the transmons have to be excited at different frequencies ($\omega_d^1 - \omega_d^2 = \delta \neq 0$). From \eqref{eq:RWA} we find that even in the doubly-rotating frame $\hat H_{int}$ is oscillating, and it is not possible to simply drop this term in RWA because this will lead to qualitatively different results. In this case, to find the steady state of the system we employ the qutip's \textit{propagator} and \textit{propagator\_steadystate} functions. The propagator is a completely positive map $\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow \hat \rho(t_1)$ describing the time evolution of the system density matrix; for \eqref{eq:master}, it is defined as
\begin{equation}
\Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
\label{eq:propagator}
\end{equation}
where $\mathcal T$ is the time-ordering superoperator. Since the Liouvillian is periodic with a period of $T = 2\pi/\delta$, it is possible to calculate the steady state as the eigenvector $\hat \rho_{ss}$ of the single-period propagator $\Lambda(T, 0)$ corresponding to its largest eigenvalue\cite{dittrich1998quantum, rivas2012open}. Upon infinite applications of $\Lambda$
\[
\lim_{n\to \infty} \left[\Lambda(T, 0)\right]^n \hat \rho = \Lambda(nT, 0) \hat \rho \to \hat \rho_{ss}.
\]

@@

	\includegraphics[width=.55\linewidth]{stationary}
	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}. Colour shows the real part of complex transmission  through the sample. Two transmons are aligned as in \autoref{fig:experiment}~(c) and form a symmetric picture. Experimental data contain an additional horizontal line from a parasitic resonance interacting with the readout resonator. Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; other pronounced features reproduced by the modelling are shown with numbered markers (see text for description). We also denote some of the transitions $00 - ij/n$ where $i,j$ stand for the final transmon energy levels and $/n$ is optional for an $n$-photon process. \textbf{(c)} Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour). Lines show various transition frequencies from the stationary Hamiltonian. The legend labels the transitions at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
	\label{fig:two-tone}
\end{figure*}

@@

Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms. We confirm this by numerically diagonalizing $\hat H_{tr}^1+\hat H_{tr}^2+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:two-tone}~(c). While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}~(a), it completely misses the Roman-numbered effects. Taking into account more energy levels for transmons does not help, and is not even necessary to reproduce the experiment, as we will show in the following.

>>>>

% ****** Start of file aipsamp.tex ****m*
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.
%
%   See the AIP README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
% 
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aipsamp
%  2)  bibtex aipsamp
%  3)  latex  aipsamp
%  4)  latex  aipsamp
%
% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 prx,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
]{revtex4-1}

@@

\renewcommand*{\figureautorefname}{Fig.}
\renewcommand*{\equationautorefname}{Eq.}

\newcommand{\mytitile}{Light-dressing of a diatomic supercondufcing artificial molecule}

@@

	\title[\mytitile]{\mytitile\\~}
	\author{G.P. Fedorov}
	\email{gleb.fedorov@phystech.edu}

	\affiliation{ 
		Russian Quantum Center, Skolkovo village, Russia
	}%
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}
	\affiliation{
		National University of Science and Technology MISIS, Moscow, Russia
	}%
	\author{V.B. Yursa}
	\affiliation{ 
		Skolkovo Institute of Science and Technology, Moscow, Russian Federation
	}%

@@

	\author{I.A. Rodionov}
	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}
	\affiliation{Dukhov Automatics Research Institute, (VNIIA), Moscow, Russia}

	\author{A.A. Dobronosova}
	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}
	\affiliation{Dukhov Automatics Research Institute, (VNIIA), Moscow, Russia}

	\author{D.O. Moskalev}
	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}

	\author{A.A. Pischimova}
	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}
	\affiliation{Dukhov Automatics Research Institute, (VNIIA), Moscow, Russia}

	\author{O.V. Astafiev}
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia 
	}
	\affiliation{Skolkovo Institute of Science and Technology, Moscow, Russian Federation}
	\affiliation{Physics Department, Royal Holloway, University of London, Egham, Surrey TW20 0EX, United Kingdom}
%

@@

	\begin{abstract}
	In this work, we study a superconducting artificial molecule composed of two magnetic-flux-tunable transmons with intense light while monitoring its state via joint dispersive readout. At certain fluxes, the molecule demonstrates a complex spectrum deviating qualitatively from the solution of the Schrödinger equation without driving. We reproduce the observed extra spectral lines accurately by numerical simulations, and find them to be a consequence of an Autler-Townes-like effect when a single tone is simultaneously dressing the system and probing the transitions between new eigenstates. We present self-consistent analytical models that account for both these processes at the same time and agree well with both experiment and numerical simulation. This study is an important step towards understanding the behaviour of more complex systems of many atoms interacting with strong radiation.
	\end{abstract}

@@

Over the past twenty years, superconducting artificial atoms (SAA) were used in numerous experiments in a compelling demonstration of the validity of fundamental quantum mechanical laws\cite{you2011atomic}. Due to synthetic nature of SAA, their Hamiltonians can be pre-designed and engineered which makes them a particularly versatile tool for studies in quantum optics. Notably, their parameters may be varied in such a wide range that novel physical effects previously inaccessible for natural systems may be directly observed.

One of the most prominent milestones, that superconducting quantum circuits have attained just in a few years after their first demonstration, is the strong coupling with light in {circuit QED}\cite{wallraff2004strong, chiorescu2004coherent} meaning that the decoherence rates are smaller than the Rabi frequency. Currently, they are surpassing all other implementations of strong coupling in terms of coherence\cite{forn2019ultrastrong}. 
However, in sharp contrast with natural atoms and molecules, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strongly to the free-propagating electromagnetic waves in 1D on-chip waveguides\cite{astafiev2010resonance} without using cavities at all. The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is even beyond strong coupling regime\cite{forn2019ultrastrong}. To correctly describe the behaviour of an atom in these conditions, the so-called \textit{dressed atom approach}\cite{cohen1998atom} is employed when the radiation has to be directly included in the Hamiltonian and affects its level structure.

So far, the main experiments in on-chip quantum optics with intense propagating light were focused on single artificial atoms\cite{baur2009measurement, sillanpaa2009autler, astafiev2010resonance, novikov2013autler, suri2013observation, koshino2013observation, braumuller2015multiphoton, peng2018vacuum, gasparinetti2019two}. In all these works, light dressing of the atom manifests itself through Mollow triplets or Autler-Townes splittings of different kinds. However, despite the recent successes in control of large arrays of interacting SAA\cite{Song574, ye2019propagation, arute2019quantum}, there were, up to our best knowledge, no experiments concerning interaction of such composite structures with intense propagating light. While studies has been done concerning dressing multi-atomic systems in a cavity\cite{fink2009dressed, macha2014implementation, shulga2017observation, yang2018probing}, their interaction with intense free radiation is also attractive since light frequency may be easily tuned to observe various absorption processes for arbitrary configurations of the system's parameters.

In this work, we study an system of two strongly coupled artificial atoms: a superconducting artificial molecule\cite{kou2017fluxonium} (SAM). We use two Xmon-type\cite{barends2013coherent} transmons\cite{koch2007charge} interacting with each other through a cavity bus\cite{majer2007coupling}. Microwave radiation is applied to this system through an on-chip coplanar waveguide while its state can be monitored by dispersive readout using the same coupling cavity\cite{chow2010detecting}. We find that strong interaction of the SAM with microwaves calls forth multiphoton transitions and Autler-Townes-like effects that could only be explained in the dressed picture. We note that although the A-T splittings have been investigated before in a wide range of quantum systems (including natural molecules\cite{tamarat1995pump, ahmed2012autler}), we find some qualitatively new spectral manifestations of the dressing effect. One of the reasons for this is that the natural molecules which could in principle demonstrate such effects do not have enough controllability and coherence. Alternatively, previous studies with SAA have either involved just a single atom or have demonstrated only the standard spectral signatures known from the quantum optics (see Appendix \ref{sec:3-level-at}).

Remarkably, besides its fundamental importance, this experiment may be useful for future quantum computers: a quantum engineer should account for the observed behaviours carefully controlling the driving power (for instance, as we will show, the bSWAP gate\cite{poletto2012entanglement} is directly affected).

The manuscript consists of four main parts and an Appendix. Section I is this introduction; Section II is devoted to the approaches that were used in our study; Section III contains the results of our experimental and theoretical research, including extensive numerical simulations and analytical analysis; finally, in Section IV we make a conclusion of our work and discuss future prospects. The Appendix contains important details of the theoretical framework that we use.

@@

\subsection{Device design and fabrication}
We have designed the SAM as a pair of transmon (Xmon) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} ($E^1_{J, \sum}/2\pi = 24.3$ GHz, $E^2_{J,\sum}/2\pi = 18.3$ GHz, $E^{1,2}_C = 220$ MHz, $d^{1,2} =0.75$) coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator ($\omega_r/2\pi \equiv f_r = 7$ GHz, $\kappa = 1/100\ \text{ns}^{-1}$) which both couples\cite{majer2007coupling} the transmons and allows the joint\cite{chow2010detecting} readout o	f their states. In \autoref{fig:experiment}~(a), the optical photograph of the device is shown depicting the layout of the components. The resonator in its upper part is connected to a coplanar waveguide through which the readout is performed. In its lower part, it is coupled to the transmons by a dual ``claw''\cite{barends2013coherent} coupler. Flux lines that allow independent control of the transmon frequencies are coming from the sides. Finally, the excitation waveguide coming from below directs microwave signal towards the SAM. In \autoref{fig:experiment}~(b) the equivalent electrical circuit of the device. The resonator fundamental mode is approximated as an LC-circuit (in the middle), the transmons are shown in colour on the sides as the LC-circuits as well, but with tunable non-linear inductances. A capacitively coupled excitation line is also shown in green. Finally, in \autoref{fig:experiment}~(c) we show schematically the frequencies of the transmons depending on the external magnetic flux. Since an effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second transmon (blue). Using both coils, it is possible to align them so that the lower sweet-spot of the orange transmon is just below the upper sweet-spot of the blue transmon (see the dashed rectangle,  \autoref{fig:experiment}~(c)). This configuration is chosen as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are close to each other in frequency. Additionally, the transmons are better protected from the flux noise in this area being close to their sweet spots.

@@

\begin{table}
	\begin{ruledtabular}
	\begin{tabular}{rll}
	Parameter & Transmon 1  & Transmon 2\\\hline
	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
	$\alpha/2\pi$ [MHz] & -220 & -220 \\
	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
	$J/2\pi$ [MHz] &\multicolumn{2}{c}{8} 
	\end{tabular}
	\end{ruledtabular}
	\caption{SAM parameters. Transmons are only different in the frequency tuning range and coherence times measured in the lower sweet spot for the 1\textsuperscript{st} one and in the higher sweet spot for the 2\textsuperscript{nd}. The coupling strength $J$ depends on the transmon frequencies and is specified here for $\omega_1 = \omega_2 = 5.32$ GHz.}
	\label{tab:parameters}
\end{table}

@@

Now, the complete Hamiltonian of SAM contains two terms describing each of them (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
\end{equation}
where $\hat H_{int} = \hbar J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms. Strictly speaking, $J = J(\omega_1, \omega_2)$ depends on the transmon frequencies\cite{koch2007charge}, but we take $J$ to be a constant as in \autoref{tab:parameters} due to its negligible variation for our range of frequencies.

For brevity, the SAM Hamiltonian without driving terms and the corresponding eigenenergies will be denoted below as ``unperturbed''.

In the following, we will also transform \autoref{Hsystem} into the frame rotating with both drives by an operator
\begin{equation}
\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}
\end{equation}
arriving at
\begin{equation}
\hat H_R = \hat R^{\dagger}\hat H \hat R -	 {i}\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
\end{equation}
Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA
\begin{equation}
\begin{aligned}
	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
	\hat H_{int} &\rightarrow \hbar J \left[\hat b^\dag \hat c e^{it(\omega_d^1 - \omega_d^2)} + \hat b \hat c^\dag e^{-it(\omega_d^1 - \omega_d^2)}\right],\\
	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

Besides the unitary evolution, we take into account the incoherent processes of relaxation and dephasing for each transmon. They are modelled using the Lindblad equation with the following collapse operators\cite{bishop2010circuit}:
\begin{equation}\
\begin{split}
\hat{{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
\hat{{O}}_{\phi, 1} = \sqrt{\gamma_{\phi,1}}\, \hat b^\dag \hat b,\\
\hat{{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
\hat{{O}}_{\phi,2} = \sqrt{\gamma_{ \phi,2}}\, \hat c^\dag \hat c,
\end{split}
\end{equation}
where $\gamma_{1,2}$ are the individual relaxation rates, and $\gamma_{\phi (1,2)}$ are the pure dephasing rates. As one can see, the collapse operators are in a separable form, i.e. acting only upon a single transmon each. This is a valid approach until the coupling strength $J$ is not too large\cite{beaudoin2011dissipation}. Therefore, the complete evolution equation for the system density matrix $\hat \rho$ is
\begin{equation}
\partial_t \hat \rho = \frac{i}{\hbar}[\hat \rho, \hat H] + \sum_{\alpha, i} \mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho = \mathcal{L}\hat\rho, \label{eq:master}
\end{equation}
where $\mathcal{D}[\hat{{O}}]\hat \rho = \hat{{O}} \hat \rho \hat{{O}}^\dag - \frac{1}{2}\{ \hat{{O}}^\dag \hat{{O}}, \hat \rho\}$ and $\mathcal{L}$ is the Liouville superoperator or the Liouvillian.

@@

Numerical simulations are crucial for studying \autoref{eq:master} since is does not allow  analytical solution. Therefore, we have been using the \textit{qutip}\cite{johansson2013qutip} (quantum optics toolbox) to simulate the dynamics and find the steady state of the system for various parameter combinations of the Liouvillian.

Two distinct modes of simulation were used during the modelling. The first one is for the Liouvillians that do not explicitly depend on time (stationary case). In this case, the steady state $\hat \rho_{ss}$ of the system should be calculated from the set of linear equations obtained from \autoref{eq:master}
\begin{equation}
\partial_t \hat \rho = 0  \Rightarrow \mathcal{L} \hat \rho = 0
\end{equation}
This equation is solved with the qutip's \textit{steadystate} function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}. This method is applicable when the driving of the two transmons is at the same frequency since from \autoref{eq:RWA} follows that $\hat H_{int}$ becomes time independent when $\omega_d^1 = \omega_d^2$.

The second mode is required when it is not possible to avoid the time-dependence of the Liouvillian or if one wants to solve the master equation in the laboratory frame. For example, when the transmons have to be excited at different frequencies ($\omega_d^1 - \omega_d^2 = \delta \neq 0$), from \autoref{eq:RWA} we find that even in the doubly-rotating frame, $\hat H_{int}$ is oscillating, and it is not possible to simply drop this term in RWA because it is inherent for the SAM. In this case, to find the steady state of the system one can employ the qutip's \textit{propagator} and \textit{propagator\_steadystate} functions. The propagator is a completely positive map $\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow \hat \rho(t_1)$ describing the time evolution of the system density matrix; for \autoref{eq:master}, it is defined as
\begin{equation}
\Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
\label{eq:propagator}
\end{equation}
where $\mathcal T$ is the time-ordering superoperator. Since the Liouvillian is periodic with a period of $T = 2\pi/\delta$, it is possible to calculate the steady state as the eigenvector $\hat \rho_{ss}$ of the single-period propagator $\Lambda(T, 0)$ corresponding to its largest eigenvalue\cite{dittrich1998quantum, rivas2012open}. Upon infinite applications of $\Lambda$
\[
\lim_{n\to \infty} \left[\Lambda(T, 0)\right]^n \hat \rho = \Lambda(nT, 0) \hat \rho \to \hat \rho_{ss}.
\]

@@

	\includegraphics[width=.495\linewidth]{main_picture_slices}
	\includegraphics[width=.495\linewidth]{stationary}
	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}. Colour shows the real part of complex transmission  through the sample. Two transmons are aligned as in \autoref{fig:experiment}~(c) and form a symmetric picture. Experimental data contain an additional horizontal line from a parasitic resonance interacting with the readout resonator. Three avoided crossings not predicted by the unperturbed model are shown in insets I, II and III; other pronounced features reproduced by the modelling are shown with numbered markers (see text for description). We also denote some of the transitions $ij/n$ (see Section \ref{sec:analysis} for notation). \textbf{(c)} Slices of the spectrum at various currents: 0.365 mA (feature III), 0.411 mA (sweet spot), 0.333 mA (feature I); experiment is gray, theory is black. Spectral lines where only one SAA is excited are highlighted with the corresponding colour from \autoref{fig:experiment}. Rabi frequencies $\Omega_{1,2}$ may be extracted as FWHM of the spectral lines 10 and 01, respectively. \textbf{(d)} Simulated population of the state $\ket{10}$ ($\lg P_{\ket{10}}$ is shown with colour). Lines show various transition frequencies from the unperturbed Hamiltonian. Legend labels transitions at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
	\label{fig:two-tone}
\end{figure*}

@@

Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the Hamiltonian with no driving. We confirm this by numerically diagonalizing $\hat H_{tr}^1+\hat H_{tr}^2+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:two-tone}~(d). While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}~(a), it completely misses the Roman-numbered effects. Taking into account more energy levels for transmons does not help, and is not even necessary to reproduce the experiment, as we will show in the following.
